### 2016-03-17 Draft.tex
Use \begin and \end abstract
Replace left quotes with `

\newcommand{\adam}[1]{{\color{blue} ADAM: #1}}
\newenvironment{indpar}[1]%
     {\begin{list}{}%
             {\setlength{\leftmargin}{#1}}%
             \item[]%
     }
     {\end{list}}

@@

\section{Abstract}

Abundance estimates from animal point-count surveys require accurate estimates of detection probabilities.  The standard model for estimating detection from removal-sampled point-count surveys assumes that organisms at a survey site are detected at a constant rate.  However, the assumption of constant detection rates during surveys is often not justified.  Detection rates can be influenced by organismal behaviors, including responses to observer presence and heterogeneity among population subgroups, and also by survey methods that affect observer effort.  Failure to account for non-constant detection leads to biased estimates of detection and therefore of abundance.  Under the standard approach, detection probability is modeled by dividing the observation period into equal-duration intervals.  We instead model the detection {\it rate} in continuous time via a time-to-detection distribution embedded within a hierarchical N-mixture framework using Bayesian methods.  Our model is thus a combination of survival time-to-event analysis with unknown-N, unknown-p abundance estimation.  We apply this model to Ovenbird counts from the Chippewa National Forest and to datasets simulated under different time-to-detection patterns.  Models assuming constant detection rates produce biased estimates of detection when true detection rates vary with time, whereas models allowing for variable detection (assuming gamma, Weibull, or lognormal distributed times to detection) produce less biased estimates of the detection probability and nominal credible interval coverage.  Models ignoring detection heterogeneity across subgroups yield biased estimates of detection when such heterogeneity exists, whereas models accounting for detection heterogeneity (modeled as a mixture) return reasonable coverage rates and can outperform heterogeneity-ignorant models even when there is no heterogeneity.

@@

@@

\adam{WRITE A SPELLBINDING OPENING PARAGRAPH}

@@

Increasing hazard functions result in a probability distribution function (pdf) for $T$ that has a mode away from zero; we term these TTDDs 'peaked'.  We contrast these to decreasing hazard functions with a mode at zero, which we term 'non-peaked'.  For our purposes, the exponential TTDD is neither peaked nor non-peaked.

@@

\begin{figure}[h!]\centering
\includegraphics[width=0.98\textwidth]{Sims/SimFull/pdet_cater_correct.pdf}
\caption{\label{pdet_cater_correct} Sim 3 caterpillar plots of posterior 50\% and 95\% credible intervals for the marginal probability of detection $p^{(det)}$.  Inference models come from the same family as the dataset but may differ in the presence/absence of a mixture component.  Each column presents one family of simulated dataset.  Upper plots show non-mixture datasets; lower plots show mixture datasets.  'X' marks the expected marginal probability of detection based on true parameter values.}
\includegraphics[width=0.98\textwidth]{Sims/SimFull/pdet_cater_family.pdf}
\caption{\label{pdet_cater_family}  Sim 3 caterpillar plots of posterior 50\% and 95\% credible intervals for the marginal probability of detection $p^{(det)}$. All data and inference models include mixtures.  Each plot presents one simulated dataset.  'X' marks the expected marginal probability of detection based on true parameter values.}
\end{figure}

>>>>

\newcommand{\adam}[1]{{\color{blue} ADAM: #1}}
\newcommand{\jarad}[1]{{\color{red} #1}}
\newenvironment{indpar}[1]%
     {\begin{list}{}%
             {\setlength{\leftmargin}{#1}}%
             \item[]%
     }
     {\end{list}}

@@

\begin{abstract}

Abundance estimates from animal point-count surveys require accurate estimates of detection probabilities.  The standard model for estimating detection from removal-sampled point-count surveys assumes that organisms at a survey site are detected at a constant rate.  However, the assumption of constant detection rates during surveys is often not justified.  Detection rates can be influenced by organismal behaviors, including responses to observer presence and heterogeneity among population subgroups, and also by survey methods that affect observer effort.  Failure to account for non-constant detection leads to biased estimates of detection and therefore of abundance. \jarad{in the abstract focus on what we did} Under the standard approach, detection probability is modeled by dividing the observation period into equal-duration intervals.  We instead model the detection {\it rate} in continuous time via a time-to-detection distribution embedded within a hierarchical N-mixture framework using Bayesian methods.  Our model is thus a combination of survival time-to-event analysis with unknown-N, unknown-p abundance estimation.  We apply this model to Ovenbird counts from the Chippewa National Forest and to datasets simulated under different time-to-detection patterns.  Models assuming constant detection rates produce biased estimates of detection when true detection rates vary with time, whereas models allowing for variable detection (assuming gamma, Weibull, or lognormal distributed times to detection) produce less biased estimates of the detection probability and nominal credible interval coverage.  Models ignoring detection heterogeneity across subgroups yield biased estimates of detection when such heterogeneity exists, whereas models accounting for detection heterogeneity (modeled as a mixture) return reasonable coverage rates and can outperform heterogeneity-ignorant models even when there is no heterogeneity.

@@

\end{abstract}

@@

\adam{WRITE A SPELLBINDING OPENING PARAGRAPH}\jarad{no need to aim so high}

@@

Increasing hazard functions result in a probability distribution function (pdf) for $T$ that has a mode away from zero; we term these TTDDs `peaked'.  We contrast these to decreasing hazard functions with a mode at zero, which we term `non-peaked'.  For our purposes, the exponential TTDD is neither peaked nor non-peaked.

@@

\begin{figure}[h!]\centering
\includegraphics[width=0.98\textwidth]{Sims/SimFull/pdet_cater_correct.pdf}
\caption{\label{pdet_cater_correct} Sim 3 caterpillar plots of posterior 50\% and 95\% credible intervals for the marginal probability of detection $p^{(det)}$.  Inference models come from the same family as the dataset but may differ in the presence/absence of a mixture component.  Each column presents one family of simulated dataset.  Upper plots show non-mixture datasets; lower plots show mixture datasets.  `X' marks the expected marginal probability of detection based on true parameter values.}
\includegraphics[width=0.98\textwidth]{Sims/SimFull/pdet_cater_family.pdf}
\caption{\label{pdet_cater_family}  Sim 3 caterpillar plots of posterior 50\% and 95\% credible intervals for the marginal probability of detection $p^{(det)}$. All data and inference models include mixtures.  Each plot presents one simulated dataset.  `X' marks the expected marginal probability of detection based on true parameter values.}
\end{figure}
